---
title: "Social Media Outputs v2"
date: "2025-12-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
load(file = ".RData")
library(emmeans)
library(psych)
library(data.table)
```

# Model Comparisons ANOVA Tables, Regression Outputs, and Post-Hoc Tests

Model Comparisons

Tests between demand models with and without social media measures (i.e., BSMAS, SMEQ, and SMDS). 

smptSNDMLM = No social media covariates

smptSNDMLMSM = With covariates no interactions

smptSNDMLMInt = With covariates and interactions
```{r model comparisons 1}
anova(smptSNDMLM, smptSNDMLMSM, smptSNDMLMInt)
```

## Tests between demand models without any social media measures and with social media measures and interactions . 
```{r model comparisons 2}
anova(smptSNDMLM, smptSNDMLMSM)
```

## ANOVA tables for all three models

No Covariates
```{r ANOVA tables}
anova(smptSNDMLM, type = "marginal") |> round(3)
```

Social Media Covariates no Interactions
```{r ANOVA tables SM}
anova(smptSNDMLMSM, type = "marginal") |> round(3)
```

Social Media Covariates with Interactions with Condition
```{r ANOVA tables Int}
anova(smptSNDMLMInt, type = "marginal") |> round(3)
```

## Regression tables for all three models

No Covariates
```{r Regression Outputs}
summary(smptSNDMLM)$tTable |> round(3)
```

Social Media Covariates no Interactions
```{r Regression Outputs SM}
summary(smptSNDMLMSM)$tTable |> round(3)
```

Social Media Covariates with Interactions with Condition
```{r Regression Outputs Int}
summary(smptSNDMLMInt)$tTable |> round(3)
```

## Post-hoc contrasts for Model with No Social Media Demographics

${Q_{0}}$ by condition
```{r Simple Post-Hocs q0}
emmeans(smptSNDMLM, param = "q0", pairwise ~ condition)
```


$\alpha$ by condition
```{r Simple Post-Hocs alpha}
emmeans(smptSNDMLM, param = "alpha", pairwise ~ condition)
```

# Post-hoc contrasts for Model with Social Media Demographic Interactions

$Q_{0}$ by Condition
```{r Interactions Post-Hocs q0 Condition}
emmeans(smptSNDMLMInt, param = "q0", pairwise ~ condition)

```

$Q_{0}$ by Social Media by Condition
```{r Interactions Post-Hocs q0 SM}
emtrends(smptSNDMLMInt, param = "q0", var = "BSMAS", pairwise ~ condition)
emtrends(smptSNDMLMInt, param = "q0", var = "SMDS", pairwise ~ condition)
emtrends(smptSNDMLMInt, param = "q0", var = "SMEQ", pairwise ~ condition)
```


$\alpha$ by Condition
```{r Interactions Post-Hocs alpha Condition}
emmeans(smptSNDMLMInt, param = "alpha", pairwise ~ condition)

```

$\alpha$ by Social Media by Condition
```{r Interactions Post-Hocs alpha SM}
emtrends(smptSNDMLMInt, param = "alpha", var = "BSMAS", pairwise ~ condition)
emtrends(smptSNDMLMInt, param = "alpha", var = "SMDS", pairwise ~ condition)
emtrends(smptSNDMLMInt, param = "alpha", var = "SMEQ", pairwise ~ condition)
```

# Comparisons between Rzeszutek et al. (2025) and Koffarnus et al. (2015) models
SND = Rzeszutek et al. (2025), Simplified Exponential with Normalized Decay 

EXPD = Koffarnus et al. (2015), Exponentiated Model of Demand

## R2 and MAE values for Rzeszutek et al.
```{r Model Fits for Rzeszutek et al. Model}
"Overall R2"
1 - sum((predict(smptSNDMLM) - (smptDataClean$y))^2)/
  sum((mean((smptDataClean$y)) - (smptDataClean$y))^2)
"Individual Median R2"
individualSNDR2[!is.infinite(R2), median(R2, na.rm = TRUE)] |> round(3)
"Individual Median R2 by condition"
individualSNDR2[!is.infinite(R2), median(R2, na.rm = TRUE), by = .(condition)]
"Individual R2 range by condition"
individualSNDR2[, range(R2, na.rm = TRUE), by = .(condition)]

"Overall MAE"
mean(abs(predict(smptSNDMLM) - (smptDataClean$y))) |> round(3)
"Individual Median MAE"
individualSNDMAE[, median(MAE, na.rm = TRUE)] |> round(3)
"Individual MAE by condition"
individualSNDMAE[, median(MAE, na.rm = TRUE), by = .(condition)]
"Individual MAE range by condition"
individualSNDMAE[, range(MAE, na.rm = TRUE), by = .(condition)]
```

## R2 and MAE values for Koffarnus et al.
```{r Model Fits for Koffarnus et al. Model}
"Overall R2"
1 - sum((predict(smptEXPDMLM) - (smptDataClean$y))^2)/
  sum((mean((smptDataClean$y)) - (smptDataClean$y))^2)
"Individual Median R2"
individualEXPDR2[!is.infinite(R2), median(R2, na.rm = TRUE)] |> round(3)
"Individual Median R2 by condition"
individualEXPDR2[!is.infinite(R2), median(R2, na.rm = TRUE), by = .(condition)]
"Individual R2 range by condition"
individualEXPDR2[, range(R2, na.rm = TRUE), by = .(condition)]

"Overall MAE"
mean(abs(predict(smptEXPDMLM) - (smptDataClean$y))) |> round(3)
"Individual Median MAE"
individualEXPDMAE[, median(MAE, na.rm = TRUE)] |> round(3)
"Individual MAE by condition"
individualEXPDMAE[, median(MAE, na.rm = TRUE), by = .(condition)]
"Invdividual MAE range by condition"
individualEXPDMAE[, range(MAE, na.rm = TRUE), by = .(condition)]
```

## Correlations between Model Parameters
```{r Model Parameters, fig.height= 4, fig.width= 4}
pairs.panels(data.frame(coef(smptSNDMLM)["q0.(Intercept)"] + coef(smptSNDMLM)["q0.conditionAttention"],
                        coef(smptEXPDMLM)["q0.(Intercept)"] + coef(smptEXPDMLM)["q0.conditionAttention"]), 
             main = expression(bold("SND vs EXPD"~Q[0]~"Attention")), 
             labels = c(expression(Q[0]~"SND"),expression(Q[0]~"EXPD")), digits = 3)
pairs.panels(data.frame(coef(smptSNDMLM)["q0.(Intercept)"] + coef(smptSNDMLM)["q0.conditionAutomatic"],
                        coef(smptEXPDMLM)["q0.(Intercept)"] + coef(smptEXPDMLM)["q0.conditionAutomatic"]), 
             main = expression(bold("SND vs EXPD"~Q[0]~"Automatic")), 
             labels = c(expression(Q[0]~"SND"),expression(Q[0]~"EXPD")), digits = 3)
pairs.panels(data.frame(coef(smptSNDMLM)["q0.(Intercept)"] + coef(smptSNDMLM)["q0.conditionEscape"],
                        coef(smptEXPDMLM)["q0.(Intercept)"] + coef(smptEXPDMLM)["q0.conditionEscape"]), 
             main = expression(bold("SND vs EXPD"~Q[0]~"Escape")), 
             labels = c(expression(Q[0]~"SND"),expression(Q[0]~"EXPD")), digits = 3)
pairs.panels(data.frame(coef(smptSNDMLM)["q0.(Intercept)"] + coef(smptSNDMLM)["q0.conditionTangible"],
                        coef(smptEXPDMLM)["q0.(Intercept)"] + coef(smptEXPDMLM)["q0.conditionTangible"]), 
             main = expression(bold("SND vs EXPD"~Q[0]~"Tangible")), 
             labels = c(expression(Q[0]~"SND"),expression(Q[0]~"EXPD")), digits = 3)

pairs.panels(data.frame(coef(smptSNDMLM)["alpha.(Intercept)"] + coef(smptSNDMLM)["alpha.conditionAttention"],
                        coef(smptEXPDMLM)["alpha.(Intercept)"] + coef(smptEXPDMLM)["alpha.conditionAttention"]), 
             main = expression(bold("SND vs EXPD"~alpha~"Attention")), 
             labels = c(expression(alpha~"SND"),expression(alpha~"EXPD")), digits = 3)
pairs.panels(data.frame(coef(smptSNDMLM)["alpha.(Intercept)"] + coef(smptSNDMLM)["alpha.conditionAutomatic"],
                        coef(smptEXPDMLM)["alpha.(Intercept)"] + coef(smptEXPDMLM)["alpha.conditionAutomatic"]), 
             main = expression(bold("SND vs EXPD"~alpha~"Automatic")), 
             labels = c(expression(alpha~"SND"),expression(alpha~"EXPD")), digits = 3)
pairs.panels(data.frame(coef(smptSNDMLM)["alpha.(Intercept)"] + coef(smptSNDMLM)["alpha.conditionEscape"],
                        coef(smptEXPDMLM)["alpha.(Intercept)"] + coef(smptEXPDMLM)["alpha.conditionEscape"]), 
             main = expression(bold("SND vs EXPD"~alpha~"Escape")), 
             labels = c(expression(alpha~"SND"),expression(alpha~"EXPD")), digits = 3)
pairs.panels(data.frame(coef(smptSNDMLM)["alpha.(Intercept)"] + coef(smptSNDMLM)["alpha.conditionTangible"],
                        coef(smptEXPDMLM)["alpha.(Intercept)"] + coef(smptEXPDMLM)["alpha.conditionTangible"]), 
             main = expression(bold("SND vs EXPD"~alpha~"Tangible")), 
             labels = c(expression(alpha~"SND"),expression(alpha~"EXPD")), digits = 3)
```